Tailored Spiral In-Out Spectral-Spatial Water Suppression Pulses for Magnetic Resonance Spectroscopic Imaging

### 2020-08-06 Manuscript/Result.tex
WAG comments

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_ComputationTime}
	\caption{Studies of different parallelization parameters, where patch width is the square root of the number of $\mathbf{W}$ columns solved for simultaneously and inclusion width is the assumed range of influence of each excitation k-space location. \textbf{(a)} Computation time vs. thread numbers. Patch width and inclusion with were kept at 4 cycle/FOV. \textbf{(b\&c)} Computation time (blue axis) and NRMSE (red axis) vs. patch widths (b) and inclusion widths (c). Thread number were kept at 16 of for both design. Inclusion width was constant at 4 in (b) and patch widths were constant at 4 (solid line) and 8 (dashed line).}
	\label{fig:ComputationTime}
\end{figure}
Figure \ref{fig:ComputationTime}a shows the mean computation time versus different thread numbers. The k-space design problem held the patch and inclusion width constant at 4. The mean computation time decreases with increasing thread numbers before 12 threads, and then plateaus due to overhead. The thread number was conservatively chosen to be 16 for the following studies to ensure timely solutions. 
Figure \ref{fig:ComputationTime}b shows the mean computation time and the NRMSE with different patch widths. The computation time increases and the NRMSE decreases as the patch width increases. This was because when patch width increases, there are more excitation trajectory points included in one instance problem, even with the same inclusion width. As a result, each instance problem becomes bigger and more time consuming, which cancels the advantageous fact that there are fewer instance problems in total, especially in cases with parallel computing. Furthermore, increasing the patch width is equivalently increasing the inclusion widths for the center target points within each patch, which makes the solutions more accurate. Here, we chose patch widths 4 and 8 (labeled $2^2$ and $2^3$) to balance time and accuracy for further evaluation.
Figure \ref{fig:ComputationTime}c shows the mean computation time and the NRMSE with different inclusion widths. The solid lines and dashed lines were obtained with patch width 4 and 8, respectively. Computation time increases and error decreases with increasing inclusion width. Particularly, increasing inclusion width is equivalent to utilizing more accurate $B_1^+$ information by truncating the $B_1^+$ map Fourier transforms to zero further out from DC. For both patch widths 4 and 8, 4 is the optimal inclusion width, which confirms the result in \ref{fig:ComputationTime}a , previously. Using an inclusion width of 4, the computation time and error are acceptable for both patch width numbers. Following these results,  we chose patch width 4 for the further designs.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_ErrorMap2}
	\caption{Normalized excitation patterns (top row) and error maps (bottom row) for k-space domain design (left column) and spatial domain design (right column), with NRMSE and design time indicated.}
	\label{fig:ErrorMap}
\end{figure}
The normalized excitation patterns and error maps are shown in Fig \ref{fig:ErrorMap} for both k-space domain design (left) and spatial domain design (right), where the k-space domain design was solved with 16 parallel computing threads, patch width 4, and inclusion width 4. 
Both designs were done with the 64$\times$64$\times$48 grid size (3mm iso-resolution), and the excitation patterns were evaluated against the target pattern with the 128$\times$128$\times$96 grid size (1.5mm iso-resolution).  grid size. 
The calculated NRMSE from the k-space domain design and the spatial domain design were 5.02\% and 4.94\%, respectively, which were practically equal. For both design methods, most of the errors appeared at the edges of the transition band, with other errors lower than 5\% of the target flip angle. This indicates uniform inner volume suppression while maintaining the outer volume intact, which can in turn decrease g-factor in highly accelerated imaging. In practice, error near the transition band can be mitigated by ensuring the region of interest (ROI) of the cortex falls completely in the stop-band and assuming zero signal within the pass-band during undersampled reconstruction. More significantly, the parallelized k-space domain design method drastically reduced the mean computation time from 100.9 seconds to 2.9 seconds compared to the spatial domain design, which was a 97\% decrease.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_Acceleration}
	\caption{ Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), with excitation trajectories undersampled by different acceleration factors (third row).}
	\label{fig:kspace_PTX_Acceleration}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_B0}
	\caption{\textbf{(a)} Normalized off-resonance map with Gaussian distortion centered above the frontal sinus, mimicking a characteristic susceptibility induced $B_0$ inhomogeneity. \textbf{(b)} Normalized excitation maps and RMSE for spatial domain design with off-resonance correction (first row), k-space domain design with and without off-resonance correction (second \& third rows).}
	\label{fig:kspace_PTX_B0}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_ComputationTime}
	\caption{\textcolor{red}{WAG: Can you also run $2^0$ (most importantly) and $2^5$ patch width here? It would be good to show that the NRMSE levels off at some point. Also can you change the NRMSE axis to go from 0 to 6? That will help emphasize that even though the error is decreasing with increasing patch width, 
	the difference between patch width = 2 and patch width = something large is quite small. }
	Studies of different parallelization parameters, where patch width is the square root of the number of $\mathbf{W}$ columns solved for simultaneously and inclusion width is the assumed range of influence of each excitation k-space location. \textbf{(a)} Computation time vs. thread numbers. Patch width and inclusion with were kept at 4 cycle/FOV. \textbf{(b\&c)} Computation time (blue axis) and NRMSE (red axis) vs. patch widths (b) and inclusion widths (c). Thread number were kept at 16 of for both design. Inclusion width was constant at 4 in (b) and patch widths were constant at 4 (solid line) and 8 (dashed line).}
	\label{fig:ComputationTime}
\end{figure}
Figure \ref{fig:ComputationTime}a shows the mean computation time versus different thread numbers. The k-space design problem held the patch and inclusion width constant at 4. The mean computation time decreases with increasing thread numbers before 12 threads, and then plateaus due to overhead. The thread number was conservatively chosen to be 16 for the following studies to ensure timely solutions. 
Figure \ref{fig:ComputationTime}b shows the mean computation time and the NRMSE with different patch widths. The computation time increases and the NRMSE decreases as the patch width increases. This was because when patch width increases, there are more excitation trajectory points included in one instance problem, even with the same inclusion width. As a result, each instance problem becomes bigger and more time consuming, which cancels the advantageous fact that there are fewer instance problems in total, especially in cases with parallel computing. Furthermore, increasing the patch width is equivalently increasing the inclusion widths for the center target points within each patch, which makes the solutions more accurate. Here, we chose patch widths 4 and 8 (labeled $2^2$ and $2^3$) to balance time and accuracy for further evaluation.
Figure \ref{fig:ComputationTime}c shows the mean computation time and the NRMSE with different inclusion widths. The solid lines and dashed lines were obtained with patch width 4 and 8, respectively. Computation time increases and error decreases with increasing inclusion width. Particularly, increasing inclusion width is equivalent to utilizing more accurate $B_1^+$ information by truncating the $B_1^+$ map Fourier transforms to zero further out from DC. For both patch widths 4 and 8, 4 is the optimal inclusion width, which confirms the result in \ref{fig:ComputationTime}a , previously. Using an inclusion width of 4, the computation time and error are acceptable for both patch width numbers. Following these results,  we chose patch width 4 for the further designs.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_ErrorMap2}
	\caption{\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
	Normalized excitation patterns (top row) and error maps (bottom row) for k-space domain design (left column) and spatial domain design (right column), with NRMSE and design time indicated.}
	\label{fig:ErrorMap}
\end{figure}
The normalized excitation patterns and error maps are shown in Fig \ref{fig:ErrorMap} for both k-space domain design (left) and spatial domain design (right), where the k-space domain design was solved with 16 parallel computing threads, patch width 4, and inclusion width 4. 
Both designs were done with the 64$\times$64$\times$48 grid size (3mm iso-resolution), and the excitation patterns were evaluated against the target pattern with the 128$\times$128$\times$96 grid size (1.5mm iso-resolution).  grid size. 
The calculated NRMSE from the k-space domain design and the spatial domain design were 5.02\% and 4.94\%, respectively, which were practically equal. For both design methods, most of the errors appeared at the edges of the transition band, with other errors lower than 5\% of the target flip angle. This indicates uniform inner volume suppression while maintaining the outer volume intact, which can in turn decrease g-factor in highly accelerated imaging. In practice, error near the transition band can be mitigated by ensuring the region of interest (ROI) of the cortex falls completely in the stop-band and assuming zero signal within the pass-band during undersampled reconstruction. More significantly, the parallelized k-space domain design method drastically reduced the mean computation time from 100.9 seconds to 2.9 seconds compared to the spatial domain design, which was a 97\% decrease.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_Acceleration}
	\caption{ \textcolor{red}{We should talk about this; I don't think reviewers will like the fact that the scale starts at 0.2. Also we should probably call it `Reduction Factor' since it is 
	really the factor by which the pulse duration is reduced, and not exactly a k-space undersampling factor, is that right?}
	Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), with excitation trajectories undersampled by different acceleration factors (third row).}
	\label{fig:kspace_PTX_Acceleration}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_B0}
	\caption{\textcolor{red}{WAG: Update with new correction method; include compute times and errors versus number of segments}
	\textbf{(a)} Normalized off-resonance map with Gaussian distortion centered above the frontal sinus, mimicking a characteristic susceptibility induced $B_0$ inhomogeneity. \textbf{(b)} Normalized excitation maps and RMSE for spatial domain design with off-resonance correction (first row), k-space domain design with and without off-resonance correction (second \& third rows).}
	\label{fig:kspace_PTX_B0}
\end{figure}

### 2020-08-06 Manuscript/Theory.tex
WAG comments

\subsection*{Parallelization}
\par A key advantage of the proposed pulse design formalism is that it can be broken down into many small problems and finely parallelized, because the process of solving each column of $\mathbf{W}$ is independent of other columns. The columns can be solved fully independently, or patchwise for target locations in neighborhoods, wherein all points in the neighborhood share the same $\mathbf{S}^{H}\mathbf{S}$ matrix. 
\begin{figure}
	\centering
	\includegraphics[width=6cm]{kspace_PTX_Patch}
	\caption{Illustration of one instance within the palatalization of a 2D k-space domain design problem. The totally design problem is divided into patches of width 4 cycle/FOV, and the 16 yellow points are the target points in this instance. With inclusion width of 4 cycle/FOV, the 46 green excitation trajectory points within the 12 cycle/FOV wide green square (4 cycle/FOV extended outside of the patch) are considered in this instance. The excitation within the 20 cycle/FOV wide red patch is constrained to zero except the point where the delta function is.}
	\label{fig:Patch}
\end{figure}
An example of this concept is shown in Figure \ref{fig:Patch}. For simplicity of visualization, it is demonstrated in a 2D problem, but the concept is easily extended to 3D. The figure depicts the solution of the $\mathbf{W}$ matrix 16 columns at a time, whose corresponding delta functions live within a patch of width 4 cycle/FOV (yellow points in Figure \ref{fig:Patch}). In this instance where the inclusion width is also 4 cycle/FOV, we truncate the $B_1^+$ map Fourier transforms to zero outside a 4 by 4 cycle/FOV square centered at DC. As a result, we must consider all the excitation trajectory points within a 12 by 12 cycle/FOV square, which is 4 cycle/FOV extended outside of the patch width 4 square, since they may contribute energy to the target locations corresponding to the 16 $\mathbf{W}$ matrix columns. For a single instance of the 16-point target patch shown in Figure \ref{fig:Patch}, the 46 green points on the excitation trajectory may contribute significant energy and are considered in the weight design. Furthermore, we must constrain the total excitation to zero at all k-space locations within a 20 by 20 cycle/FOV red patch in Figure \ref{fig:Patch}. This is because any energy deposited at each considered excitation trajectory points will affect not only the target points in the yellow square, but also the whole 2$\times$4 wide patch around that trajectory point. And the 20 by 20 cycle/FOV red patch is the total of the points that can be affected by all the excitation trajectory points considered in this instance. Therefore, in the solution for this instance, $\mathbf{w}$ is a 46$N_c\times$16 matrix, $\mathbf{S}$ is a 400$N_c\times$46$N_c$ matrix, $\mathbf{S}^{H}\mathbf{S}$ is a 46$N_c\times$46$N_c$ matrix, and $\mathbf{s}_i^{H}$ is a 46$N_c\times$16 matrix. 
%Since $\mathbf{s}_i^{H}$ is no longer related to the $i$th row of $\mathbf{S}$ and $i$th column of $\mathbf{W}$ only, it will be denoted as $\mathbf{S_{targ}}$ in later discussions. 
In the next instance, another 16 columns centered around another 4 points by 4 points patch will be solved. It should be noted that in different instances, the number of neighboring excitation trajectory points (the 46 green points in the previous instance) can vary. We will denote this number of points by $N_n$. $N_n$ can be zero when a patch is at the corners where no excitation trajectory point is adjacent. 
%For patches near edges of the excitation k-space FOV, the solution neighborhood and area may wrap back in a circulant shift fashion, depending on the resolution of the final spatial grid on which the user will evaluate the pulse. In Figure \ref{fig:Patch}), denoted by the red area to the right of Figure \ref{fig:Patch}).

>>>>

\subsection*{Parallelization}
\par A key advantage of the proposed pulse design formalism is that it can be broken down into many small problems and finely parallelized, because the process of solving each column of $\mathbf{W}$ is independent of other columns. The columns can be solved fully independently, or patchwise for target locations in neighborhoods, wherein all points in the neighborhood share the same $\mathbf{S}^{H}\mathbf{S}$ matrix. 
\begin{figure}
	\centering
	\includegraphics[width=6cm]{kspace_PTX_Patch}
	\caption{\textcolor{red}{WAG: I think you should make two subfigures here: one that illustrates a single target location, and one that illustrates a patch of target locations. Also you should annotate the different widths, in the figures, with arrows. Also add a legend for the dots} 
	Illustration of one instance within the palatalization of a 2D k-space domain design problem. The totally design problem is divided into patches of width 4 cycle/FOV, and the 16 yellow points are the target points in this instance. With inclusion width of 4 cycle/FOV, the 46 green excitation trajectory points within the 12 cycle/FOV wide green square (4 cycle/FOV extended outside of the patch) are considered in this instance. The excitation within the 20 cycle/FOV wide red patch is constrained to zero except the point where the delta function is.}
	\label{fig:Patch}
\end{figure}
An example of this concept is shown in Figure \ref{fig:Patch}. For simplicity of visualization, it is demonstrated in a 2D problem, but the concept is easily extended to 3D. The figure depicts the solution of the $\mathbf{W}$ matrix 16 columns at a time, whose corresponding delta functions live within a patch of width 4 cycle/FOV (yellow points in Figure \ref{fig:Patch}). In this instance where the inclusion width is also 4 cycle/FOV, we truncate the $B_1^+$ map Fourier transforms to zero outside a 4 by 4 cycle/FOV square centered at DC. As a result, we must consider all the excitation trajectory points within a 12 by 12 cycle/FOV square, which is 4 cycle/FOV extended outside of the patch width 4 square, since they may contribute energy to the target locations corresponding to the 16 $\mathbf{W}$ matrix columns. For a single instance of the 16-point target patch shown in Figure \ref{fig:Patch}, the 46 green points on the excitation trajectory may contribute significant energy and are considered in the weight design. Furthermore, we must constrain the total excitation to zero at all k-space locations within a 20 by 20 cycle/FOV red patch in Figure \ref{fig:Patch}. This is because any energy deposited at each considered excitation trajectory points will affect not only the target points in the yellow square, but also the whole 2$\times$4 wide patch around that trajectory point. And the 20 by 20 cycle/FOV red patch is the total of the points that can be affected by all the excitation trajectory points considered in this instance. Therefore, in the solution for this instance, $\mathbf{w}$ is a 46$N_c\times$16 matrix, $\mathbf{S}$ is a 400$N_c\times$46$N_c$ matrix, $\mathbf{S}^{H}\mathbf{S}$ is a 46$N_c\times$46$N_c$ matrix, and $\mathbf{s}_i^{H}$ is a 46$N_c\times$16 matrix. 
%Since $\mathbf{s}_i^{H}$ is no longer related to the $i$th row of $\mathbf{S}$ and $i$th column of $\mathbf{W}$ only, it will be denoted as $\mathbf{S_{targ}}$ in later discussions. 
In the next instance, another 16 columns centered around another 4 points by 4 points patch will be solved. It should be noted that in different instances, the number of neighboring excitation trajectory points (the 46 green points in the previous instance) can vary. We will denote this number of points by $N_n$. $N_n$ can be zero when a patch is at the corners where no excitation trajectory point is adjacent. 
%For patches near edges of the excitation k-space FOV, the solution neighborhood and area may wrap back in a circulant shift fashion, depending on the resolution of the final spatial grid on which the user will evaluate the pulse. In Figure \ref{fig:Patch}), denoted by the red area to the right of Figure \ref{fig:Patch}).
